%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%                                                                 %
%                         ACKNOWLEDGEMENT                         %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 
\specialhead{ACKNOWLEDGMENT}
Many people have helped to bring this thesis to fruition, and must be recognized. First are collaborators Michael Aldersley and Prakash Joshi who helped prepare the samples used through the course of this work, and have provided much advice through the course of this research project over the past few years. I would also like to thank some of our collaborators at Corning Inc, particularly Aravind Rammohan and Ross Stewart, with whom I have had many fruitful conversations, and who helped with starting the molecular dynamics simulations. Another priceless resources through this project was Siddharth Sundararaman, who was instrumental in getting the molecular dynamics simulations off the ground.

There are many people in my life who have played a large role in my success at RPI, and helped me complete this thesis. I would first like to thank all of my friends here at RPI who have made the stressful school life here far more palatable. Without all of you, I would have surely gone crazy, and the long nights working on homework would have been far longer.

Great appreciation is also extended to the French department at SUNY Albany for being so accepting and accommodating in the many French classes which I took there during my time at RPI. A special thanks is extended Professor Susan Blood, who helped foster and encourage my learning in French language and literature, and with whom I was able to spend many hours conversing on topics in French history and literature. Without these experiences, I would be far less prepared to begin further studies in France than I am now.

Next are my parents who have put up with my perpetually being away from home for most of the past five years. Their encouragement, and love however has been an absolutely critical component in the completion of this work. I also thank them for their further acceptance of my being away from home, as I prepare to move abroad for my PhD.

Lastly, I would like to thank the Physics department here at RPI. All of the professors have been the leading instrument in my formation as a physicist thus far. This is especially true of Professor Wilke, who has supported, encouraged, instructed, and advised me over the past five years. I will truly miss our hours of discussion on my research and various other topics. Her advice in preparing this manuscript and applying to graduate schools has been more than instrumental in helping me achieve my goals, and I cannot thank her enough.